Collective excitations in competing phases in two and three dimensions

### 2024-01-11 paper/main.tex
home

Lastly, we investigate the same spectral functions close to the AFM-CDW phase transition, depicted in \autoref{fig:resolvent_overview_AFM}.
We choose $V=1t$ for both lattices and $U=zV \pm 0.1t$, where $z$ is the coordination number, see panels (a) and (b).
Again, both SC-related spectral functions are identical in both the CDW and AFM phases.
Within the continuum their weight is shifted towards the upper edge and on the square lattice only, there is a peak above the continuum.
In the AFM phase, both $\spectral{AFM}$ and $\spectral{CDW}$ have a peak close, but yet below, the two-particle continuum.
The peak of the former is at a lower energy than the peak of the latter.
In the CDW phase, this behavior is reversed, i.e., the peak in $\spectral{CDW}$ lies lower.
Using the same analysis as before, we conclude that each of these peaks is a $\delta$ peak.
Moving further away from the phase transition, here $U=z(V+0.2t)$ in panels (c) and (d), the upper peak becomes soft as it shifts into the quasiparticle continuum.

>>>>

Lastly, we investigate the same spectral functions close to the AFM-CDW phase transition, depicted in \autoref{fig:resolvent_overview_AFM}.
We choose $V=1t$ for both lattices and $U=zV \pm 0.1t$, where $z$ is the coordination number, see panels (a) and (b).
Again, both SC-related spectral functions are identical in both the CDW and AFM phases.
Within the continuum their weight is shifted towards the upper edge and on the square lattice only, there is a peak above the continuum.
In the AFM phase, both $\spectral{AFM}$ and $\spectral{CDW}$ have a peak close, but yet below, the two-particle continuum.
The peak of the former is at a lower energy than the peak of the latter.
In the CDW phase, this behavior is reversed, i.e., the peak in $\spectral{CDW}$ lies lower.
Using the same analysis as before, we conclude that each of these peaks is a $\delta$ peak.
Moving further away from the phase transition, here $U=z(V+0.2t)$ in panels (c) and (d), the upper peak becomes soft as it shifts into the two-particle continuum.
